A Low-cost Natural Interaction based on a Camera Hand-Gestures Recognizer

### 2011-01-24 paper.tex
fix figure position

\subsection{Gestures Library}
We have analyzed some talk-shows in order to extract important gestures being performed, and defining a benchmark scenario. 
We have tried to target the following kinds of gestures in a first step:

@@

@@

\newpage
\section{Technical Work}
Pipeline of the work:
\png{pipeline}{Pipeline of work components}

>>>>

\subsection{Gestures Library}

@@

We have analyzed some talk-shows in order to extract important gestures being performed, and defining a benchmark scenario. 
%We have tried to target the following kinds of gestures in a first step.

@@

\section{Technical Work}
Pipeline of the work:
\png{pipeline}{Pipeline of work components}
